---
title: "dplyr filter homework"
author: "Robert Risti"
date: "2019-03-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Exercises

Loading required libraries:
```{r}
library(tidyverse)
library(here)
```

Importing dataset:
```{r}
viruses <- read_csv(here("data", "viruses.csv"))
```

Print out dataset:
```{r}
viruses
```


1. Find all viruses that:

- have genome of over 10000kb

```{r}
genome_10kb <- filter(viruses, size_kb > 10000)
genome_10kb
```

- belong to *Papillomaviridae*

```{r}
papillo <- filter(viruses, 	subgroup == "Papillomaviridae")
papillo
```

- are from plants and environment

```{r}
custom_group <- filter(viruses, host == "environment" | host == "plants")
custom_group
```

- were released between 01. January 1980 - 01. January 1990, including these days:

```{r}
library(lubridate)
date <- filter(viruses, (year(release_date) >= 1980 && year(release_date) <= 1990))
date

```

2. there is also between() function in dplyr. 

What does it do? Run ?between
How can you use it to find viruses with genomes between 1 to 2 kb?

```{r}
genome_1_2kb <- filter(viruses, between(size_kb,1,2))
genome_1_2kb
```

3. Find Enteroviruses:

Hint: use str_detect()
```{r}
library(stringr)
entero <- filter(viruses, str_detect(organism_name,".?nterovirus")) 
entero
#Ignoring first letter because some names are capitalized and some are not
```

